Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-15 paper/manuscript.tex
edits to Methods about TMPRSS2

\subsection*{Creation of MDCK-SIAT1-TMPRSS2 cell line}
The human TMPRSS2 cDNA ORF was ordered from OriGene (NM\_005656), PCR amplified, and cloned into a pHAGE2 lentiviral vector under an EF1$\alpha$-Int promoter and attached to mCherry through an IRES. 
We generated lentiviruses..etc etc transduced MDCK-SIAT1 cells, sorted by fluorescence activated cell sorting
\comment{Need to look at Katie's notebooks for this...}

>>>>

\subsection*{Creation of MDCK-SIAT1-TMPRSS2 cell line}
\comment{A sentence or two about the rationale: Normally trypsin must be added. In order to obviate the need for trypsin.}
The human TMPRSS2 cDNA ORF was ordered from OriGene (NM\_005656), PCR amplified, and cloned into a pHAGE2 lentiviral vector under an EF1$\alpha$-Int promoter followed by an IRES driving expression of mCherry.
We used the lentiviral vector to transduce MDCK-SIAT1 cells, and sorted an intermediate mCherry population by flow cytometry.
We refer to the resulting bulk population of sorted cells as MDCK-SIAT1-TMPRSS2 cells.
There is no selectable marker for the TMPRSS2; however, we generally maintain the cells at low passage number, and have seen no indication that lose their ability to support the replication of viruses with H3 HAs in the absence of exogenous trypsin.
